---
title: 'Basic R'
author: "Sanaz Eghbali"
---

## Question 1

a) Use the `seq()` function to create the vector $(1, 7, 13, \ldots, 61)$. Note that each term in this sequence is of the form 
$1 + 6n$ where $n = 0, \ldots, 10$.

```{r}
seq(1,61, by=6)
```

b) Use `seq()` and `c()` to create the vector $(1, 2, 3, \ldots, 10, 9, 8, \ldots, 3, 2, 1)$.

```{r}
c(seq(1,10),seq(9,1))
```

c) Use `rep()` to create the vector $(2,3,4,\dots,2,3,4)$ in which the sequence $(2,3,4)$ is repeated 5 times.

```{r}
rep(2:4 ,5)
```

d) Use `rep()` to create the vector $(1,1,\ldots,1,2,2,\ldots,2,3,3,\ldots,3)$ where each number is repeated 7 times.

```{r}
rep(1:3, each=7)
```

e) Use `rep()` to create the vector $(10,20,20,30,30,30,\ldots,100,\ldots,100)$ where $10n$ is repeated $n$ times.

```{r}
rep(seq(10,100, by=10),(1:10))
```

## Question 2

a) Compute: $$\sum_{n=1}^{100} n$$

```{r}
sum(seq(1:100))
```

b) Compute: $$\sum_{n=10}^{100} n^3$$

```{r}
sum(seq(10:100)^3)
```

c) Compute: $$\sum_{n=1}^{10}\left(\frac{2^{n}}{n} + \frac{4^{n}}{n^{4}}\right)$$

```{r}
n<- 1:10
sum((2^n/n)+(4^n/n^4))
```

d) Compute: $$\sum_{n=0}^{10} \frac{1}{n!}$$ 
Hint: Use `factorial(n)` to compute $n!$

```{r}
sum(1/(factorial(0:10)))
```

e) Compute: $$\sum_{n=1}^{20} \left(2n + \frac{1}{\sqrt{n}}\right)$$

```{r}
n<- 1:20
sum((2*n)+(1/(sqrt(n))))
```


## Question 3

a) Create an empty list `mylist`.

```{r}
mylist<-c()
mylist
```

b) Add a component named `aa` whose value is 42.

```{r}
mylist$aa<-42
mylist$aa
```

c) Add a component named `bb` whose value is the numeric vector $(1,2,\ldots,10)$.

```{r}
mylist$bb<-(1:10)
mylist$bb
```

d) Add a component named `cc` whose value is the character vector ("Hello", "CIND 123").

```{r}
mylist$cc<- c("Hello", "CIND 123")
mylist$cc
```

e) Add a component named `dd` whose value is a 4x3 matrix whose elements are $(1,2,\ldots,12)$ in row-wise order.

```{r}
mylist$dd<- matrix(1:12,nrow =4, byrow =TRUE)
mylist$dd
```

f) Display `mylist` on the screen.

```{r}
mylist
```

## Question 4

If you have not already done so, install the ISwR package on
your computer using the command `install.packages("ISwR")`.

Load the `ISwR` package into your session.
```{r}
library(ISwR)
```

a) Display the last 6 rows of the `thuesen` data frame.

```{r}
tail(thuesen, n=6 )
```

b) Compute the mean of each variable using `sapply()` function.

Hint: You might need to consider removing the `NA` values, otherwise the average will not be computed.

```{r}
sapply(thuesen, mean, na.rm=TRUE)
```

c) Create a numeric vectors `v1`, `v2`, and `v3` whose elements are the numbers from 1 to 20, their squares, and their square-roots respectiverly.

```{r}
v1<- as.numeric(c(1:20))
v1
v2<- c(v1^2)
v2
v3<- c(sqrt(v1))
v3
```

d) Create a new data frame `iData` by combining the `v1`, `v2`, and `v3` together in a column-wise perspective.

```{r}
iData <- data.frame(v1, v2, v3)
iData
```

e) Display the first quartile of `iData`.

```{r}
sapply(iData, function(x)quantile(x, probs=0.25))
```

f) Create a 5x5 empty matrix, i.e. all elements equal to NA, and fill the diagonal from the top left corner to the bottom right corner of `mat1' with the values 'This' 'is' 'the' 'main' 'diagonal' then display mat1.
```{r}
mat1 <- matrix(nr=5, nc=5)
diag(mat1) <- c("This", "is", "the", "main", "diagonal")
mat1
```
